Some examples in extended logic counting classes

### 2016-12-02 LICS/beyond.tex
paper v.1

We also define the set of transitive $\qso$ formulas ($\tqso$-formulas) using the following grammar:
\begin{multline*}
%	\label{eq-def-tqso}
	\alpha := \varphi \ \mid \ s \ \mid \ (\alpha \add \alpha) \ \mid\ (\alpha \mult \alpha) \ \mid \\ \sa{x} \alpha \ \mid \ \pa{x} \alpha \ \mid \ \sa{X} \alpha \ \mid \ \pa{X} \alpha \ \mid \ [\pth \varphi]
\end{multline*}
where $\varphi$ is an $\so$-formula over $\R$, $s \in \bbN$, $x \in \fv$ and $X \in \sv$.
\begin{theorem}
	Given a positive $\fo$ formula $\varphi(\bar{x},R)$ and a $\qfo$ formula $\alpha(\bar{x})$, there exists a $\qso$ formula $\beta(\bar{x})$ such that $\sem{[\alfp\varphi(\bar{x},R)\mid \alpha(\bar{x},R)](\bar{x})} = \sem{\beta(\bar{x})}$.
\end{theorem}

\begin{theorem}
	$\tqfo(\fo)$ captures $\shl$ over the class of ordered structures.
\end{theorem}

\begin{theorem}
	$\tqso(\fo)$ captures $\shp$ over the class of ordered structures.
\end{theorem}

@@

\begin{theorem}
	$\rqfo(\fo)$ captures $\fp$ over the class of ordered structures.
\end{theorem}

>>>>

We also define the set of transitive $\qso$ formulas ($\tqso$-formulas) using the following grammar:
\begin{multline*}
%	\label{eq-def-tqso}
	\alpha := \varphi \ \mid \ s \ \mid \ (\alpha \add \alpha) \ \mid\ (\alpha \mult \alpha) \ \mid \\ \sa{x} \alpha \ \mid \ \pa{x} \alpha \ \mid \ \sa{X} \alpha \ \mid \ \pa{X} \alpha \ \mid \ [\pth \varphi]
\end{multline*}
where $\varphi$ is an $\so$-formula over $\R$, $s \in \bbN$, $x \in \fv$ and $X \in \sv$.
\begin{theorem} \label{so-rec}
	Given a positive $\fo$ formula $\varphi(\bar{x},R)$ and a $\qfo$ formula $\alpha(\bar{x})$, there exists a $\qso$ formula $\beta(\bar{x})$ such that $\sem{[\alfp\varphi(\bar{x},R)\mid \alpha(\bar{x},R)](\bar{x})} = \sem{\beta(\bar{x})}$.
\end{theorem}

\begin{theorem} \label{tqfo-fo-cap}
	$\tqfo(\fo)$ captures $\shl$ over the class of ordered structures.
\end{theorem}

\begin{theorem} \label{tqso-fo-cap}
	$\tqso(\fo)$ captures $\shp$ over the class of ordered structures.
\end{theorem}

@@

\begin{theorem} \label{rqfo-fo-cap}
	$\rqfo(\fo)$ captures $\fp$ over the class of ordered structures.
\end{theorem}

### 2016-12-02 LICS/counting.tex
paper v.1

\begin{theorem}
	$\qfo(\pfp)$ captures $\nfpspace$ over the class of ordered structures.
\end{theorem}

\begin{theorem}
	$\tqso(\fo)$ captures $\shp$ over the class of ordered structures.
\end{theorem}

\begin{theorem}
	($\qfo(\lfp)$ or $\qfo(\fo)$) with algebraic least fixed point operator captures $\totp$ over the class of ordered structures.
\end{theorem}

\begin{theorem}
	$\eqso(\fo)$ captures $\shp$ over the class of ordered structures.
\end{theorem}

\begin{proposition}
	$\eqso(\fo)$ does not capture $\shp$ over the class of all structures.
\end{proposition}

\begin{theorem}
	$\eqso(\integ,\fo)$ captures $\gp$ over the class of ordered structures.
\end{theorem}

\begin{theorem}
	$\eqso(\eso)$ captures $\spp$ over the class of ordered structures.
\end{theorem}

>>>>

\begin{theorem} \label{qfo-pfp-cap}
	$\qfo(\pfp)$ captures $\nfpspace$ over the class of ordered structures.
\end{theorem}

\begin{theorem} \label{eqso-fo-cap}
	$\eqso(\fo)$ captures $\shp$ over the class of ordered structures.
\end{theorem}

\begin{proposition} \label{eqso-fo-cap-not}
	$\eqso(\fo)$ does not capture $\shp$ over the class of all structures.
\end{proposition}

\begin{theorem} \label{eqso-eso-cap}
	$\eqso(\eso)$ captures $\spp$ over the class of ordered structures.
\end{theorem}

### 2016-12-02 LICS/syntactic.tex
paper v.1

\begin{theorem}
	If $\E1$ is closed under substraction, then {\sc P} = {\sc NP}.
\end{theorem}

\begin{theorem}
	$\#\Sigma_1 \subsetneq \E1$
\end{theorem}

@@

\begin{theorem}
	$\XE{1}$ is closed under substraction by one.
\end{theorem}

\begin{theorem}
	{\sc \#DNF} is hard for $\E1$ under parsimonious reductions. 
\end{theorem}

\begin{theorem}
	$\U{1}$ with $n$ open first-order variables is properly contained in $\U{1}$ with $n+1$ open first-order variables for $n\in\N$.  
\end{theorem}

@@

\begin{theorem}
	$\HE{2} \subseteq \pe$
\end{theorem}

>>>>

\begin{theorem} \label{sub-pnp}
	If $\E1$ is closed under substraction, then {\sc P} = {\sc NP}.
\end{theorem}

\begin{theorem} \label{sigma1strict}
	$\#\Sigma_1 \subsetneq \E1$
\end{theorem}

@@

\begin{theorem} \label{sigmafo-minusone}
	$\XE{1}$ is closed under substraction by one.
\end{theorem}

\begin{theorem} \label{dnf-pars}
	{\sc \#DNF} is hard for $\E1$ under parsimonious reductions. 
\end{theorem}

\begin{theorem} \label{nplusone-strict}
	$\U{1}$ with $n$ open first-order variables is properly contained in $\U{1}$ with $n+1$ open first-order variables for $n\in\N$.  
\end{theorem}

@@

\begin{theorem} \label{sigma2-pe}
	$\HE{2} \subseteq \pe$
\end{theorem}
